Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-26 src/article.tex
Update conclusion.

    At the end, a comparison was made of the approaches considered, from which it can be seen that
    the SPLADE method has the highest accuracy, followed by the compressed RepBERT, but this
    approach are less effective due to the fact that it is based on dense representations.

    The information provided will be used for further research.
    Our focus will be more on sparse representations for the first stage of information retrieval.
    In further works, it is assumed that we have our own stand for researching deep learning
    models in order to form an index in an information retrieval system.

>>>>

    At the end, a comparison was made of the approaches considered, from which it can be seen that
    the SPLADE method has the highest accuracy, followed by the RepBERT, but this
    approach are less effective due to the fact that it is based on dense representations the
    embeddings for which are stored in a relatively slow vector database.
    However, SPLADE is slower to learn than SparTerm due to the use of negative sampling.

    In further works, it is assumed that we have our own stand.
    The obtained stand is planned to be used for further research, the purpose of which is to
    develop an algorithm based on sparse representations with a search accuracy similar to
    current state-of-the-art, but requiring less computational resources and memory.
